Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-11-02 manuscript/manuscript.Rmd
caught mistake in reported post-hoc t-test

get_d <- function(Predictor, Multi_Condition = "Consistent") {
  linear_mod <- lm(
    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)

  ifelse(Multi_Condition == "Consistent",
         parse_number(apa_results$table$statistic[2])/sqrt(499),
         parse_number(apa_results$table$statistic[3])/sqrt(500)) 
}

@@

t_test <- apa_print(t.test(df_multiconsistent$Final_beliefs,
                           df_multiconsistent$Prior_beliefs, 
                           paired = TRUE))

cohens_d <- parse_number(gsub(".*=", "", t_test$statistic)) / sqrt(499)

t_apa <- paste(t_test$estimate, 
               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
               sep = ", ")

# Post-hoc t-test
df_multi_inconsistent <- df %>% 
  filter(Condition == "Multi-inconsistent")

t_test <- apa_print(t.test(df_multi_inconsistent$Final_beliefs,
                           df_multi_inconsistent$Prior_beliefs, 
                           paired = TRUE))

t_apa <- paste(t_test$estimate, 
               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
               sep = ", ")

# Post-hoc t-test
df_single <- df %>% 
  filter(Condition == "Single")

t_test <- apa_print(t.test(df_single$Final_beliefs,
                           df_single$Prior_beliefs, 
                           paired = TRUE))

>>>>

@@

t_test <- apa_print(
  t.test(
    df_multiconsistent$Final_beliefs,
    df_multiconsistent$Prior_beliefs, 
    paired = TRUE))
